Enhancement of SDR in Thessaloniki

### 2024-04-21 GHI_enh_03_process.tex
Commit 2024-04-21 22:14

C4 factor: 1.03 
C4 offset: 15 
\end{verbatim}

@@

\begin{verbatim}
2024-04-21 13:51:37.8 athan@sagan GHI_enh_02_ID_CE.R 14.833272 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -9.187e+01  4.952e+01  -1.855   0.0644 .  
as.numeric(Date)  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-384.81 -144.57  -53.50   96.68  768.76

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -9.187e+01  4.952e+01  -1.855   0.0644 .  
ST_E_monthly$Date  3.286e-07  3.958e-08   8.302 2.08e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 211.4 on 361 degrees of freedom
Multiple R-squared:  0.1603,    Adjusted R-squared:  0.158 
F-statistic: 68.92 on 1 and 361 DF,  p-value: 2.077e-15
\end{verbatim}

@@

\begin{verbatim}
2024-04-21 13:57:31.4 athan@sagan GHI_enh_02_ID_CE.R 3.765186 mins
\end{verbatim}

>>>>

C4 factor: 1.04 
C4 offset: 15 
\end{verbatim}

@@

\begin{verbatim}
2024-04-21 16:10:56.4 athan@tyler GHI_enh_02_ID_CE.R 27.296893 mins
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-349.43 -124.67  -47.48   83.61  668.69

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -8.500e+01  4.348e+01  -1.955   0.0514 .  
as.numeric(Date)  2.911e-07  3.473e-08   8.383 1.18e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 185 on 360 degrees of freedom
Multiple R-squared:  0.1633,    Adjusted R-squared:  0.161 
F-statistic: 70.27 on 1 and 360 DF,  p-value: 1.182e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-349.43 -124.67  -47.48   83.61  668.69

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -8.500e+01  4.348e+01  -1.955   0.0514 .  
ST_E_monthly$Date  2.911e-07  3.473e-08   8.383 1.18e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 185 on 360 degrees of freedom
Multiple R-squared:  0.1633,    Adjusted R-squared:  0.161 
F-statistic: 70.27 on 1 and 360 DF,  p-value: 1.182e-15
\end{verbatim}

@@

\begin{verbatim}
2024-04-21 16:22:21.3 athan@tyler GHI_enh_02_ID_CE.R 8.808619 mins
\end{verbatim}
